An Embedding Framework for Consistent Polyhedral Surrogates

### 2019-05-23 neurips-19/poly-embed.tex
abstain!

\usetikzlibrary{calc}
\newcommand{\Comments}{1}
\newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
\newcommand{\mytodo}[2]{\ifnum\Comments=1%
  \todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\raf}[1]{\mynote{green}{[RF: #1]}}
\newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}
\newcommand{\jessie}[1]{\mynote{purple}{[JF: #1]}}
\newcommand{\jessiet}[1]{\mytodo{purple!20!white}{JF: #1}}
\newcommand{\bo}[1]{\mynote{blue}{[Bo: #1]}}
\newcommand{\botodo}[1]{\mytodo{blue!20!white}{[Bo: #1]}}
\newcommand{\btw}[1]{\mytodo{gray}{#1}}
\ifnum\Comments=1               % fix margins for todonotes
  \setlength{\marginparwidth}{1in}
\fi

@@

\newcommand{\hinge}{L_{\mathrm{hinge}}}
\newcommand{\ellzo}{\ell_{\text{0-1}}}

@@

Our results give a framework to construct consistent surrogates and link functions, but they also provide a way to verify the consistency or inconsistency of given surrogates.
Below, we illustrate the power of this framework with specific examples from the literature, as well as new examples.
In some cases we simplify existing proofs, while in others we give new results, such as the inconsistency of the recently proposed Lov\'asz hinge.
\raf{Notes to self: The top-k and hypercube/set examples (except abstain) have the link built in, e.g.\ as the sign function), and they just work around it.  Our results may suggest that it's worth thinking ``outside the box'' (HAH, genious...) and looking for embeddings which are not the hypercube.}

\subsection{Consistency of abstain surrogate and link construction}
\label{sec:abstain}
\raf{Jessie: could you add the definition of their surrogate and link?  Use eq:abstain-surrogate for the label}
Consider the $\abstain{1/2}$ property, where one wants to report the most likely outcome, conditioned on such a $p_y \geq 1/2$.
If there is no such $p_y$, then the $\abstain{1/2}$ property suggests we abstain from predicting any one outcome.

~\citet{ramaswamy2018consistent} provides a consistent, polyhedral surrogate for a particular case of the abstain loss $\ell_{\abstain{\alpha}}:[n] \cup \{a\} \to \reals$ defined:
\begin{align}\label{eq:abstain-discrete}
\ell_{\abstain{\alpha}}(r,y) := \begin{cases}
0 & r = y\\
\alpha & r = a\\
1 & \text{otherwise}
\end{cases}
\end{align}
Here, the report $a$ corresponds to ``abstaining'' from voting if the outcome of any outcome is not likely enough to occur.

The $\abstain{1/2}$ surrogate provided by Ramaswamy et al.~\cite{ramaswamy2018consistent} embeds the $n$ outcomes into the $n$ vertices of the $d := \ceil{\log_2(n)}$-dimensional hypercube (vertices in $\{\pm 1\}^n$), and embeds the abstain point at the origin.
They give the surrogate
\begin{equation}\label{eq:abstain-surrogate}
L_{\abstain{1/2}}(u, y) = \left(\max_{j \in [d]}\varphi(y)_j u_j + 1\right)_+
\end{equation}
Moreover, they go on to show consistency and provide a link function from their surrogate to $\ell_{\abstain{1/2}}$.
\begin{equation}\label{eq:abstain-link}
	\phi(u) = \begin{cases}
	a & \min_{i \in [d]} |u_i| \leq 1/2\\
	\varphi^{-1}(\sgn(-u)) &\text{otherwise}
	\end{cases}
\end{equation}
\jessiet{Note about how they have $\sgn(0) = 1$?}

@@

The construction given in Theorem~\ref{thm:discrete-loss-poly-embeddable}, together with the calibrated link construction in Section~\ref{sec:calibration}, can generate consistent convex surrogates for arbitrary discrete losses.
For example, consider cost-sensitive classification; given an arbitrary loss matrix $C \in \reals^{n\times n}_+$ describing the loss $\ell_j(i) = C_{ij}$ of predicting label $i$ when the true label is $j$, we construct a convex surrogate based on the convex conjugate of $-\risk{\ell}$.
While of course several surrogates are known for this problem~\cite{pires2013cost}, they typically work in $n$ dimensions.
%\raf{Jessie, could you cite \url{http://proceedings.mlr.press/v28/avilapires13.pdf} here}
one advantage of our embedding framework is the ability to construct lower-dimensional surrogates when costs have certain geometric interpretations.
For example, if $v_1,\ldots,v_n \in \reals^k$ are on the unit sphere and $C_{ij} = \inprod{v_i}{v_j}$, we can simply take $L_j(u) = $\raf{aaaand Noah woke up}

>>>>

\usetikzlibrary{calc}
\newcommand{\Comments}{1}
\newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
\newcommand{\mytodo}[2]{\ifnum\Comments=1%
  \todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\raf}[1]{\mynote{green}{[RF: #1]}}
\newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}
\newcommand{\jessie}[1]{\mynote{purple}{[JF: #1]}}
\newcommand{\jessiet}[1]{\mytodo{purple!20!white}{JF: #1}}
\newcommand{\bo}[1]{\mynote{blue}{[Bo: #1]}}
\newcommand{\botodo}[1]{\mytodo{blue!20!white}{[Bo: #1]}}
\newcommand{\btw}[1]{}%TURN OFF FOR NOW \mytodo{gray}{#1}}
\ifnum\Comments=1               % fix margins for todonotes
  \setlength{\marginparwidth}{1in}
\fi

@@

\newcommand{\hinge}{L_{\mathrm{hinge}}}
\newcommand{\ellzo}{\ell_{\text{0-1}}}
\newcommand{\ellabs}[1]{\ell_{#1}}

@@

Our results give a framework to construct consistent surrogates and link functions, but they also provide a way to verify the consistency or inconsistency of given surrogates.
Below, we illustrate the power of this framework with specific examples from the literature, as well as new examples.
In some cases we simplify existing proofs, while in others we give new results, such as a new calibrated link for abstain loss, and the inconsistency of the recently proposed Lov\'asz hinge.
\btw{RF: The top-k and hypercube/set examples (except abstain) have the link built in, e.g.\ as the sign function), and they just work around it.  Our results may suggest that it's worth thinking ``outside the box'' (HAH, genious...) and looking for embeddings which are not the hypercube.}

\subsection{Consistency of abstain surrogate and link construction}
\label{sec:abstain}

In classification settings with a large number of labels, several authors consider a variant of classification, with the addition of a ``reject'' or \emph{abstain} option.
For example, \citet{ramaswamy2018consistent} study the loss $\ellabs{\alpha} : [n] \cup \{\bot\} \to \reals^\Y_+$ defined by
\begin{align}\label{eq:abstain-discrete}
\ellabs{\alpha}(r)_y = \begin{cases}
0 & r = y\\
\alpha & r = \bot\\
1 & \text{otherwise}
\end{cases}~.
\end{align}
Here, the report $\bot$ corresponds to ``abstaining'' if no label is sufficiently likely, specifically, if no $y\in\Y$ has $p_y \geq 1-\alpha$.
\citet{ramaswamy2018consistent} provide a polyhedral surrogate for $\ellabs{\alpha}$, which we present here for $\alpha=1/2$.
Letting $d = \ceil{\log_2(n)}$ their surrogate is $L_{1/2} : \reals^d \to \reals^\Y_+$ given by
\begin{equation}\label{eq:abstain-surrogate}
L_{1/2}(u)_y = \left(\max_{j \in [d]}B(y)_j u_j + 1\right)_+~,
\end{equation}
where $B:[n]\to\{-1,1\}^d$ is a arbitrary injection; let us assume $n = 2^d$ so that we have a bijection.
Consistency is proven for the following link function,
\begin{equation}\label{eq:abstain-link}
  \psi(u) = \begin{cases}
	\bot & \min_{i \in [d]} |u_i| \leq 1/2\\
	B^{-1}(\sgn(-u)) &\text{otherwise}
  \end{cases}~.
\end{equation}

In light of our framework, we can see that $L_{1/2}$ is an excellent example of an embedding, where $\varphi(y) = B(y)$ and $\varphi(\bot) = 0 \in \reals^d$.
Moreover, the link function $\psi$ is exactly the link obtained from Theorem\raf{ref Bo's stuff} with the norm being $\|\cdot\|_\infty$ and $\epsilon=1/2$.
We show the full construction of $\Psi$ in Figure\raf{ref}, as well as a valid resolution yielding $\psi$.
Thus, our framework would have simplified the process of finding such a link function.

To illustrate this point further, we give an alternate link $\psi_1$ generated from Theorem\raf{ref Bo's stuff} for $\|\cdot\|_1$ and $\epsilon=1$, shown in Figure\raf{ref}:
\begin{equation}\label{eq:abstain-link}
  \psi_1(u) = \begin{cases}
	\bot & \|u\|_1 \leq 1\\
	B^{-1}(\sgn(-u)) &\text{otherwise}
  \end{cases}~.
\end{equation}
In particular, Theorem\raf{ref Bo's stuff} gives us calibration of $(L_{1/2},\psi_1)$ with respect to $\ellabs{1/2}$.
Aside from its simplicity, one possible advantage of $\psi_1$ is that it appears to yield the same constant in generalization bounds as $\psi$, yet assigns $\bot$ to much less of the surrogate space $\reals^d$.
It would be interesting to compare the two links in practice.

@@

\raf{I think we should cut this subsection, and maybe just remind the reader at the prelude to this section that Theorem~\ref{thm:discrete-loss-poly-embeddable} gives a construction for any discrete loss.}
The construction given in Theorem~\ref{thm:discrete-loss-poly-embeddable}, together with the calibrated link construction in Section~\ref{sec:calibration}, can generate consistent convex surrogates for arbitrary discrete losses.
For example, consider cost-sensitive classification; given an arbitrary loss matrix $C \in \reals^{n\times n}_+$ describing the loss $\ell_j(i) = C_{ij}$ of predicting label $i$ when the true label is $j$, we construct a convex surrogate based on the convex conjugate of $-\risk{\ell}$.
While of course several surrogates are known for this problem~\cite{pires2013cost}, they typically work in $n$ dimensions.
%\raf{Jessie, could you cite \url{http://proceedings.mlr.press/v28/avilapires13.pdf} here}
one advantage of our embedding framework is the ability to construct lower-dimensional surrogates when costs have certain geometric interpretations.
For example, if $v_1,\ldots,v_n \in \reals^k$ are on the unit sphere and $C_{ij} = \inprod{v_i}{v_j}$, we can simply take $L_j(u) = $\raf{aaaand Noah woke up}\raf{Just realized that this loss matrix has rank $k$ and thus is covered by AA15: just elicit the linear property $\E v_Y \in \reals^k$.}
